Multi sky-view\\ 3D aerosol distribution recovery

### 2013-10-03 article.tex
bookmark

%\hl{Thickening the aerosols density ten folds in the} {\em Haze Blobs} \hl{scene
%resulted in a larger local error, i.e. $\epsilon=0.98$ (compared to $\epsilon=0.65$).
%This admits to the fact that the single-scattering model, on which the reconstruction
%algorithm is based, is valid when the optical depth of the medium is small.}
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/simulation_particles.pdf}}
  \caption{\small MC simulations of the {\em Haze Blobs} scene
    with varying density scales and aerosol characteristics
    (described in \cref{sec:optimization-results}). All images
    correspond to the same viewpoint of
    \ref{fig:simulation-results1}(d). (a) low density scale
    (b) absorbing particle, (c) isotropic particle and (d) high
    density scale.
  }
  \label{fig:simulation_particles}
\end{figure}
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/reconstructions.pdf}}
  \caption{\small 
    Reconstructions of the scenes shown in
    \cref{fig:simulation_particles}(b)--(d).
    (1a absorbing particle, (b) isotropic particle and (c) high
    density scale scenes, respectively.}
  \label{fig:reconstructions}
\end{figure}

>>>>

%\hl{Thickening the aerosols density ten folds in the} {\em Haze Blobs} \hl{scene
%resulted in a larger local error, i.e. $\epsilon=0.98$ (compared to $\epsilon=0.65$).
%This admits to the fact that the single-scattering model, on which the reconstruction
%algorithm is based, is valid when the optical depth of the medium is small.}
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/simulation_particles.pdf}}
  \caption{\small MC simulations of the {\em Haze Blobs} scene
    with varying density scales and aerosol characteristics
    (described in \cref{sec:optimization-results}). All images
    correspond to the same viewpoint of
    \ref{fig:simulation-results1}(d). (a) low density scale
    (b) absorbing particle, (c) isotropic particle and (d) high
    density scale.
  }
  \label{fig:simulation_particles}
\end{figure}
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/reconstructions.pdf}}
  \caption{\small 
    Reconstructions of the scenes shown in
    Figs.~\ref{fig:simulation_particles}(b)--(d).
    (a) absorbing particle scene, (b) isotropic particle scene
    and (c) high density scale scene, respectively.}
  \label{fig:reconstructions}
\end{figure}
